Import packages

```{r}

library(RCurl)
library(foreign)
library(lpSolve)

```

Import and show the file

```{r}
baby.food <- read.csv('Baby Food.csv', header = TRUE, skip = 1)
baby.food

```

Objective Function

```{r}
cost <- c(baby.food[,2])

```

Constraints

#1. Calories: 1 month old female needs 438 calories per day.
```{r}
rhs.constraint<- c(438)*-1
lhs.constraint <- rbind(c(baby.food[,3])*-1)
```

#2. Carbs: From 0-6 month olds need at least 60 carbs per day
```{r}
rhs.carb.constraint <- c(60)*-1
rhs.constraint <- c(rhs.constraint, rhs.carb.constraint)

lhs.carb.constraint <- c(baby.food[,7])*-1
lhs.constraint <- rbind(lhs.constraint, lhs.carb.constraint)
```

#3. Protein: From 0-6 months old need at least 9.1 grams of protein
```{r}
rhs.protein.constraint <- c(9.1)*-1
rhs.constraint <- c(rhs.constraint, rhs.protein.constraint)

lhs.protein.constraint <- c(baby.food[,10])*-1
lhs.constraint <- rbind(lhs.constraint, lhs.protein.constraint)
```

#4. Vitamin A: Goal is to hit 100% Vitamin A; check with Dr. if % on product
matches needs 0-6 month old
```{r}
rhs.vitaminA.constraint <- c(1)*-1
rhs.constraint <- c(rhs.constraint, rhs.vitaminA.constraint)

lhs.vitaminA.constraint <- c(baby.food[,11])*-1
lhs.constraint <- rbind(lhs.constraint, lhs.vitaminA.constraint)
```

#5. Vitamin C: Goal is to hit 100% Vitamin C; check with Dr. if % on product matches needs 0-6 month old
```{r}
rhs.vitaminC.constraint <- c(1)*-1
rhs.constraint <- c(rhs.constraint, rhs.vitaminC.constraint)

lhs.vitaminC.constraint <- c(baby.food[,12])*-1
lhs.constraint <- rbind(lhs.constraint, lhs.vitaminC.constraint)
```


Solving the linear model
```{r}
library(linprog)
answer <- solveLP(cost, rhs.constraint, lhs.constraint, maximum = FALSE)
```


```{R}
answer$opt
```
```{R}
answer$solution
```


```{R}
answer$con
```


```{R}
answer
```

